
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex,colorlinks = true,
urlcolor  = blue,]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeMyItem}[1]{
  \item\small{
    \ #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Tarun Pothulapati} & Email : \href{mailto:tarunpothulapati@outlook.com}{tarunpothulapati@outlook.com}\\
  \href{http://tarrooon.com/}{www.tarrooon.com} & Mobile : +91-9398529136 \\
  \href{http://linkedin.com/in/tpothulapati}{LinkedIn}\hspace{10mm}
  \href{http://www.github.com/pothulapati}{GitHub}\hspace{10mm}
  \href{http://www.twitter.com/tarrooon}{Twitter}
\end{tabular*}

%-----------WORK Experience-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Senior Software Engineer, Gitpod}{Remote}
{Golang, Kubernetes}{February. 2022 -- Jan. 2023}
\resumeItemListStart
\resumeMyItem{Part of the \textbf{Delivery Team}, and Helped build the \textbf{self-hosted installation of Gitpod} on Kubernetes with
  monthly release cadence along with a focus on automated testing pipelines, telemetry, etc. }
\resumeMyItem{Worked on a preview version of Gitpod which \textbf{packaged the full Gitpod experience in a single docker container} for self-serve enterprise users.}
\resumeMyItem{Helped various teams in \textbf{being confident with their part of delivery, by building tools} for upgrades
  clusters, components catering both to the SAAS instance, and self-hosted users.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer, Buoyant}{Remote}
{Linkerd, CNCF Incubated OSS Service Mesh project}{March. 2020 -- January 2022}
\resumeItemListStart
\resumeMyItem{\textbf{Linkerd Maintainer}, focusing on the control-plane written in Golang.}
\resumeMyItem{Worked on various e2e features like the extensions, new upgrade flow, etc starting from the \textbf{design phase all the
    way till integration tests}.}
\resumeMyItem{Played a key role in moving the \textbf{CLI logic to use Helm package internally}, and thus having only one logic to
  support thereby \textbf{reducing maintainer burden}.}
\resumeMyItem{Helped move SMI functionality into a separate extension, by writing a controller that converts SMI resources into
  resouces that Linkerd can understand. This helped in \textbf{having better separation of conerns}.}
\resumeMyItem{Pariticipated in \textbf{various OSS project outreach activities} like Documentation, Technical talks/blogs, Slack
  support, etc.}

\resumeItemListEnd
\resumeSubheading
{Intern, Community Bridge Program}{Remote}
{Linkerd and Jaeger, Cloud Native Computing Foundation(CNCF)}{October. 2019 -- Present}
\resumeItemListStart
\resumeMyItem{Working on adding Distributed Tracing Support to Linkerd with Open Telemetry and Jaeger as the components. }
\resumeMyItem{Working on an add-on model for Linkerd, to provide Out-of-box experience both through Helm and Linkerd CLI. }
\resumeItemListEnd

\resumeSubheading
{Google Summer Of Code 2019}{Remote}
{Linkerd, Cloud Native Computing Foundation(CNCF) Incubated Project}{May. 2019 -- September. 2019}
\resumeItemListStart
\resumeMyItem{Worked on implementing Service Mesh Interface (SMI) Metrics spec for Istio, Consul and also making the project more extensible.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://github.com/Pothulapati/gh-action-trace}{gh-action-trace}}{}
{Rust, tracing, Jaeger}{}
\resumeItemListStart
\resumeMyItem{A CLI to generate traces for GitHub Action runs by retrieving the metadata from GitHub API.}
\resumeMyItem{Useful to understand the overall timings of GitHub Action runs and in understanding where things are slow.}
\resumeItemListEnd

\resumeSubheading
{\href{https://github.com/Pothulapati/doker}{Doker}}{}
{Golang, Client-Go, Docker, Kubernetes}{}
\resumeItemListStart
\resumeMyItem{Do\textbf{k}er is a cli tool that provides a docker-cli experience but for a Kubernetes Cluster}
\resumeMyItem{It allows users to manage Images and Containers on the Kubernetes nodes by running a daemonset which interacts with the docker daemon.}
\resumeItemListEnd

\resumeSubheading
{\href{https://github.com/Pothulapati/tsep}{Tsep: Telangana State Eamcet Predictor}}{}
{C\#, Asp.Net Core, Azure Table Storage, Azure App Service}{}
\resumeItemListStart
\resumeMyItem{Developed a Web Application which predicted ranks and colleges for students according to their score in EAMCET (Engineering Agricultural and Medical Common Entrance Test).}
\resumeMyItem{The prediction is almost accurate as it is based upon previous years data and analytics.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TALKS-----------------
\section{Technical Talks}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://www.youtube.com/watch?v=pZnNvU89wes&feature=youtu.be}{How Linkerd Transforms Code into running Software}}{at GitHub Satellite India 2021}
\resumeSubItem{\href{https://www.youtube.com/watch?v=rYp0bUmcbMs}{Piecing together Rust: It is more than just writing code}}{at RustFest Global 2020}
\resumeSubItem{\href{https://www.youtube.com/watch?v=9XlEIURv_3M}{Overview and State of Linkerd}}{at KubeCon + CloudNativeCon North America 2020}
\resumeSubItem{CNCF Hyderabad Meetup Group}{ Part of the organising team, to have an active community around Cloud Native Technologies in Hyderabad. }
\resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Vardhaman College Of Engineering}{Hyderabad, India}
{Bachelor of Technology in Computer Science;  CGPA: 9.16 }{Aug. 2016 -- March. 2020}
\resumeSubheading
{Sri Chaitanya Junior College}{Hyderabad, India}
{Intermediate: Maths, Physics and Chemistry;  95.1\% }{Jun. 2014 -- March. 2016}
\resumeSubHeadingListEnd



%-----------AWARDS-----------------
\section{Awards and Recognitions}
\resumeSubHeadingListStart
\resumeSubItem{KubeCon + CloudNativeCon NA 2019}{Was awarded scholarship to attend the conference which happened in \textbf{San Diego, Califoria, USA} on \textbf{18th November 2019}.}
\resumeSubItem{KubeCon + CloudNativeCon EU 2019}{Was awarded scholarship to attend the conference which happened in \textbf{Barcelona, Spain} on \textbf{21st May 2019}.}
\resumeSubItem{Megathon 2017, IIIT Hyderabad}
{Won 1st Prize in the IBM Challenge for developing an IT Service Chatbot using IBM Watson and Microsoft Bot Framework.}
\resumeSubItem{AICTE All India Startup Contest 2017, Chennai }
{Was one of the top 40 finalists across the Country.}
\resumeSubItem{IEEE SS12 National Level Competition 2017 , Hyderabad }
{Won the second prize for developing Dr.Bot, a healthcare assistant.}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------

\section{Certifications}
\resumeSubHeadingListStart
\resumeSubItem{Certified Kubernetes Administrator}{Successfully completed CKA certification by Cloud Native Computing
  Foundation (CNCF) in February, 2020.}
\resumeSubItem{Cambridge Businss English Vantage certification}
{Scored 176/190.}
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages And Frameworks}{Go, Rust, Python, C\#, Java, SQL, .Net Core, Asp.Net Core}
\resumeSubItem{Technologies}{Kubernetes, Networking, Cloud Computing, Distributed Systems, Linux, Git, NoSQL}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}